% LaTeX resume example template
%
% Matthew M. Boedicker <matthewm@boedicker.org>
% http://matthewm.boedicker.org/
%
% placed in the public domain

\documentclass[11pt]{article}
\usepackage[top=0.9in, bottom=0.1in, left=0.6in, right=0.6in]{geometry}
%\usepackage{fullpage}
\textheight=9.0in
\pagestyle{empty}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{1in}
\usepackage{CJK}
\usepackage{enumitem}
\setenumerate[1]{itemsep=1pt,partopsep=1pt,parsep=\parskip,topsep=5pt}
\setitemize[1]{itemsep=0pt,partopsep=0pt,parsep=\parskip,topsep=5pt}
\setdescription{itemsep=0pt,partopsep=0pt,parsep=\parskip,topsep=5pt}
\begin{document}
\begin{CJK}{GBK}{kai}
\begin{center}
  {\textbf{\huge Honghui Zhang}}\\\bigskip
  1323 W Dayton St Apt 109, Madison, WI 53715, USA\\
  +1 (650)296-6720, zhhthu11@gmail.com\\
\end{center}
\rule[4pt]{18.5cm}{0.5pt}
{ \textbf{\underline{Education}}}\\\medskip
\begin{itemize}
  \item \textbf{University of Wisconsin-Madison}, Madison, WI, USA\\
  Master of Science, Computer Science  \hfill Aug. 2015 - Dec. 2016\\
    \begin{itemize}
    \item admitted with graduate scholarship and CS scholarship
    \item teaching assistant for CS540 (Intro to AI) and CS367 (Intro to Data Structures)\\\medskip
    \end{itemize}
 \item \textbf{Tsinghua University}, Beijing, China\\
 Bachelor of Engineering. Computer Science \hfill Aug. 2011 - Jul. 2015\\
    \begin{itemize}
    \item cumulative GPA: \textbf{91/100}, Four-Scale GPA: \textbf{3.90/4.00}
    \item graduated with First Honor (\textbf{top2\%})
    \end{itemize}
\end{itemize}

\bigskip

{\textbf{\underline{Work Experience}}}\\\medskip

\begin{itemize}
%   \item \textbf{Software Engineering Intern}, Facebook Inc, California, United States \hfill May. 2016 - Aug. 2016\\
%     \begin{itemize}
%     \item The project will be determined in April 2016. \\\medskip
%     \end{itemize}

   \item \textbf{Research Intern}, Microsoft Research Asia, Beijing, China \hfill Dec. 2014 - Apr. 2015\\
     \begin{itemize}
     \item Developed an IR-based algorithm to retrieve original articles based on screenshots with the Knowledge Mining Group. Improved accuracy of prediction from 67\% to 95\%.
     \item Obtained The Award of Excellence of The Stars of Tomorrow Internship Program.\\\medskip
     \end{itemize}

   \item \textbf{Summer Research Intern}, University of Illinois at Chicago, United States \hfill Jul. 2014 - Sep. 2014\\
     \begin{itemize}
     \item Inferred diffusion network  by structure transfer learning and proposed a unified optimization framework TrNetInf, which performed excellently in real-world datasets.
     \item Related work has been published in an international conference DASFAA2015. \\\medskip
     \end{itemize}
  
   \item \textbf{Research Assistant}, Tsinghua University, Beijing, China \hfill Sep. 2013 - Jul. 2015\\
     \begin{itemize}
     %\item Developed a time-aware personalized recommendation based on text mining in large-scale user reviews and time series analysis. 
     \item Developed an NLP-based algorithm to aggregate aspects from online reviews into a hierarchy, achieving more than 20\% accuracy when compared to traditional methods. 
     %\item Related work has been published in an international conference WWW2015.
     \item Obtained Excellent Undergraduate Thesis of Tsinghua University (top2\%)
     \end{itemize}
\end{itemize}

\bigskip

{ \textbf{\underline{Awards}}}\\
\begin{itemize}
\item Hackillinois Sponsored Prize - Most Interesting Use of Search \hfill Feb. 2016
\item 3rd Place, ACM/ICPC Programming Contest, North America Regional \hfill Oct. 2015
\item Excellent Undergraduate of Tsinghua University (top2\%, \textbf{First Honor}) \hfill Jul. 2015
\item Excellent Academic Awards of Tsinghua University (top2\%) \hfill 2012 - 2014
\item Excellent Undergraduate of China Computer Federation \hfill Oct. 2013
\item First Prize in National Olympiad in Informatics in Provinces \hfill Sep. 2010
\end{itemize}

\bigskip

{ \textbf{\underline{Publication}}}
\begin{itemize}
    \item Senzhang Wang, \textbf{Honghui Zhang}, Jiawei Zhang, Philip S. Yu, Zhoujun Li \\ \textbf{Inferring Diffusion Network with Sparse Cascades by Structure Transfer}\\ The 20th International Conference on Database Systems for Advanced Applications (DASFAA’15)
\end{itemize}

\end{CJK}
\end{document}
